\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Small changes to Sec 4-5.  Clarify design challenges in Sec 6.1.

\begin{itemize}
\item {\bfseries Technical terms:} The interface uses technical and Tor-specific terms that are likely unfamiliar to an average user (e.g., ``Tor network,'' ``local proxy,'' ``bridges,'' and ``transports''). 
\item {\bfseries Too many choices:}  Users who do not need a bridge or proxy are able to configure them.
There are nine choices for bridges and more options to input a custom bridge.
Almost any HTTP or SOCKS proxy can be used as the proxy.
Custom bridge lines require the bridge information in a specific syntax, but this syntax is not specified in the interface.
Proxy fields also do not provide syntactic guidelines.
The full list of possible errors we identified can be found in Appendix~\ref{states}.
\item {\bfseries Poor feedback:} Even if there was a syntactic error in the bridge or proxy fields, the user is not notified until after a connection is attempted and fails. If a censored bridge was chosen, the connection timeout takes several minutes. Error messages were often technical and did not give suggestions for next steps.
\end{itemize}

@@

As we performed the experiments, we distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3. We ensured that each condition had new and previous Tor Browser users, and tried for variation in gender and age.

@@

Before beginning our procedure, we obtained informed consent from all our participants (Appendix~\ref{qualitative-script}). The session began with the participant visiting sample websites in a non-Tor browser to ascertain that some sites were blocked. The participants' task was to complete a worksheet (Appendix~\ref{participant-worksheet}) that required visiting a censored website (Wikipedia) and an uncensored website (CNN). We chose Wikipedia and CNN because of their likely familiarity~\cite{alexa}. After giving the instructions, the researchers left the room to minimize interactions and watched a live feed of the participant's screen.

@@

These were our general observations. Participants who could connect directly (E1) or use the recommended bridge had an easy time connecting (E2), but the participants who could not use many of the hardcoded bridges (E3) did not know what to do. For a summary of how each participant connected to Tor and what behavioral trends dominated in each environment, see Appendix~\ref{summary}.

@@

\begin{itemize}
\item {\bfseries User consent}: Some oppressive regimes may detect and prosecute Tor usage, and therefore simply using Tor may carry risks. While we could help users by automating configuration settings, this would involve probing network configurations, which may alert authorities to Tor usage. Taking this risk without proper consent is not ethical.

@@

\item {\bfseries Passive adversaries}: A sufficiently powerful network adversary can detect that a user is connecting to Tor. We should allow users to leverage local information to reduce their risk.

>>>>

\begin{itemize}
\item {\bfseries Technical terms:} The interface uses technical and Tor-specific terms that are likely unfamiliar to an average user (e.g., ``Tor network,'' ``local proxy,'' ``bridges,'' and ``transports''). 
\item {\bfseries Too many choices:}  Users who do not need a bridge or proxy are able to configure them.
There are nine choices for bridges and more options to input a custom bridge.
Almost any HTTP or SOCKS proxy can be used as the proxy.
Custom bridge lines require the bridge information in a specific syntax, but this syntax is not specified in the interface.
Proxy fields also do not provide syntactic guidelines.
The full list of possible errors we identified can be found in Appendix~\ref{states}.
\item {\bfseries Poor feedback:} Even if there was a syntactic error in the bridge or proxy fields, the user is not notified until after a connection is attempted and fails. If a censored bridge was chosen, the connection timeout takes several minutes. Error messages were often technical and did not suggest how to fix the problem.
\end{itemize}

@@

As we performed the experiments, we distributed participants evenly across three experimental conditions:  5~in E1, 5~in E2, and 6~in E3. We ensured that each condition had new and previous Tor Browser users, and tried for variation in gender and age.

@@

Before beginning our procedure, we obtained informed consent from all our participants (Appendix~\ref{qualitative-script}). The session began with the participant visiting sample websites in a non-Tor browser to ascertain that some sites were blocked. The participants' task was to complete a worksheet (Appendix~\ref{participant-worksheet}) that required visiting a censored website (Wikipedia) and an uncensored website (CNN). We chose Wikipedia and CNN because of their likely familiarity~\cite{alexa}. After giving the instructions, the researchers left the room to minimize interaction and watched a live feed of the participant's screen.

@@

Participants who could connect directly (E1) or use the recommended bridge had an easy time connecting (E2), but the participants who could not use many of the hardcoded bridges (E3) did not know what to do. For a summary of how each participant connected to Tor and what behavioral trends dominated in each environment, see Appendix~\ref{summary}.

@@

\begin{itemize}
\item {\bfseries User consent}: Some oppressive regimes may detect and prosecute Tor usage, and therefore simply using Tor may carry risks. While we could help users by automating configuration settings, this would involve probing network configurations and sending network traffic that could allow authorities to detect that the user is using Tor. Taking this risk without proper consent is not ethical.

@@

\item {\bfseries Passive adversaries}: A sufficiently powerful network adversary can detect that a user is connecting to Tor, unless the user chooses some very specific network configurations. We should enable informed users who wish to avoid this risk to do so.
